### 2016-10-02 introduction.tex
I'm sorry, but you can't use verb use here.
Ondrej told me that "use" - means "depend on".  Please be consistent
and don't break your own rules.

Python is a dynamically typed programming language that has a focus on
ease of use and readability.\footnote{\label{note:python}This paper assumes a moderate
  familiarity with the Python programming language.} Due in part to this focus, it has become a popular
language for scientific
computing and data science, with a broad ecosystem of
libraries~\cite{oliphant2007python}. SymPy is itself used by many libraries
and tools to support research within a variety of domains, such as
SageMath~\cite{sagemath} (pure and applied mathematics),
yt~\cite{2011ApJS..192....9T} (astronomy and astrophysics),
PyDy~\cite{gede2013constrained} (multibody dynamics), and
SfePy~\cite{cimrman2014sfepy} (finite elements).

>>>>

Python is a dynamically typed programming language that has a focus on
ease of use and readability.\footnote{\label{note:python}This paper assumes a moderate
  familiarity with the Python programming language.} Due in part to this focus, it has become a popular
language for scientific
computing and data science, with a broad ecosystem of
libraries~\cite{oliphant2007python}. SymPy is itself used as a dependency
by many libraries
and tools to support research within a variety of domains, such as
SageMath~\cite{sagemath} (pure and applied mathematics),
yt~\cite{2011ApJS..192....9T} (astronomy and astrophysics),
PyDy~\cite{gede2013constrained} (multibody dynamics), and
SfePy~\cite{cimrman2014sfepy} (finite elements).
